On Secure Delegation of SampBQP with a Classical Client

### 2019-11-23 preliminaries.tex
Fix typo
Remove unused definitions

\begin{definition}
	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$. I.e. $\Lambda^2{1, 2}(X_3)$ would be a Toffoli (CCNOT) gate.
\end{definition}

\begin{definition}
	Let $H_1, \ldots, H_n:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitians each acting on at most $k$ qubits, then $$H=\sum_{j=1}^nH_j$$ is called a \emph{$k$-local Hamiltonian}.
\end{definition}

@@

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ defined in the same way as in $\QPIP_{XZ}$ except that $\bbV$ is fully classical and cannot receive or measure qubits.
\end{definition}

>>>>

\begin{definition}
	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$. I.e. $\Lambda^2_{1, 2}(X_3)$ would be a Toffoli (CCNOT) gate.
\end{definition}

@@
